SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-13 scipy-1.0/paper.tex
Extend background section to include widening of Numeric ecosystem

% Paul Dubois, CDAT
% https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html

@@

%With a rich programming environment and a numerical array object in
%place, the time was ripe for the development of a full scientific
%software stack.

@@

%https://mail.python.org/pipermail/scipy-dev/2002-June/001007.html

>>>>

With a rich programming environment and a numerical array object in
place, the time was ripe for the development of a full scientific
software stack.  Many of the first efforts were driven by graduate
students and post-doctoral researchers, but soon attracted the
attention of senior researchers.

% Paul Dubois, CDAT
% https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html
Paul Dubois in the Program for Climate Model Diagnosis and
Intercomparison at Lawrence Livermore National Laboratory built their
Climate Data Analysis Tools (``an open-source set of Python modules
and tools for accessing, manipulating, and plotting scientific data in
general and climate data sets in
particular''\footnote{https://mail.python.org/pipermail/numpy-discussion/2001-May/000645.html})
on Numeric, the newly established Python array object.  Paul later
became the maintainer for Numeric, and helped fund the writing of the
first manual [citation needed].

@@

@@

% https://mail.python.org/pipermail/scipy-dev/2002-June/001007.html
% https://str.llnl.gov/str/News896.html
